Flexibility of interactions depends on habitat suitability

### 2019-08-26 paper/manuscript.Rmd
Add model comparison table to paper

We found that our models performe
We found that environmental suitability is an important variable

>>>>

We found that our models performed relativelly well. 
Overall we found no relationship between 
We found that environmental suitability is an important variable

```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*4, fig.cap = "Conditional effects"}
readd(fig_conditional_effects)
```

```{r model-comparison-table}
loadd(model_ranking)
waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic)

loo_scores <- as.data.frame(model_ranking$loo) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, elpd_diff, se_diff,  looic)

loo_scores %>%
  dplyr::inner_join(waic_scores, by = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>%
  knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,1,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the widely applicable information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
```
